\cvevent{ Junior Actuary }{| ERGO }{ 01/2022 -- 04/2023  }{ Cologne }{ Health Insurance }
\begin{itemize}
\item Automatisation and testing of  actuarial computations in R.
\item Developing GUIs for automated actuarial workflows.
\item Implementing a CI/CD pipeline.
\end{itemize}
\quad\cvtag{ R }\cvtag{ Shiny }\cvtag{ GitHub }\newline
\cvevent{ Research Assistent }{| Technical University  }{ 01/2022 -- 01/2023  }{ Munich }{ Research }
\begin{itemize}
\item Publishing my master’s thesis as a paper in SIAM.
\item Building a CI/CD pipeline for the implemented algorithm.
\end{itemize}
\quad\cvtag{ Python }\cvtag{ GitHub }\newline
\cvevent{ Working Student }{| MEAG }{ 01/2021 -- 01/2022  }{ Munich }{ Asset Management }
\begin{itemize}
\item Automatic parsing and compiling of risk data pertaining to financial assets in R.
\item Automatic visualisation of risk metrics in PowerBi, PowerPoint and HTML reports in R.
\item Creating custom R packages including unit testing and documentation.
\end{itemize}
\quad\cvtag{ R }\cvtag{ Tidyverse  }\cvtag{ Azure DevOps }\newline
\cvevent{ Master’s Thesis }{| Technical University }{ 01/2021 -- 01/2022  }{ Munich }{ Research }
\begin{itemize}
\item Development of a state of the art rare event estimation method.
\item Implementation as a professional Python package.
\item Using containerisation to run numerical experiments on the Google Cloud.
\end{itemize}
\quad\cvtag{ Python }\cvtag{ Docker }\newline
\cvevent{ Joint Research Project }{| Technical University  and Continental Automotive }{ 01/2020 -- 01/2021  }{ Munich }{ Research }
\begin{itemize}
\item Mathematical modelling of an autopilot.
\item Finding the best trajectory through multiple traffic lights.
\item Solving an optimal control problem.
\end{itemize}
\quad\cvtag{ MATLAB }\cvtag{ LaTeX }\newline
\cvevent{ Working Student }{| Cevotec }{ 01/2019 -- 01/2019  }{ Munich }{ Robotics }
\begin{itemize}
\item Implementation and parallelisation of optimisation algorithms in C++.
\item Development of new optimisation methods for fibre patch placement
\item Development of unit and integration tests.
\end{itemize}
\quad\cvtag{ C++ }\cvtag{ Jira }\cvtag{ Bitbucket }\newline
\cvevent{ Research Assistent }{| Technical University  }{ 01/2019 -- 01/2019  }{ Munich }{ Research }
\begin{itemize}
\item Implementation of a time integrator in Julia based on my bachelor’s thesis.
\item Contribution to the scientific computing project  DifferentialEquations.jl
\item Basis for one of the fastest state of the art explicit extrapolation methods.
\end{itemize}
\quad\cvtag{ Julia }\cvtag{ GitHub }\newline
\cvevent{ Internship }{| BMW }{ 01/2018 -- 01/2018  }{ Munich }{ Automotive }
\begin{itemize}
\item Error analysis of coupled systems in MATLAB.
\item Scientific research on the topic of model order reduction.
\item Documentation of research results with LaTeX.
\end{itemize}
\quad\cvtag{ MATLAB }\cvtag{ LaTeX }\newline